Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
update the CCT confidence intervals in application
Swicth from HC3 to NN variance estimator. The changes to CIs are very
small, no edit in the text needed.

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                      & ATE     & \multicolumn{2}{r}{95\% CI}            &     &  $h$ &   $b$ & p-value \\
    \midrule
    LM (2007)         & --1.895 & (--3.930                    & 0.139)   & 9   &      &       & 0.036 \\
    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18  &      &       & 0.081 \\
    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
    CCT               & --3.795 & (--6.885                    & --0.706) & 3   & .888 & 6.807 &       \\ 
    Wild bootstrap    & --3.800 & (--6.781                    & --0.408) & 3   & .888 & 6.807 &       \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on mortality. The first three
    rows come from Table 3 in \cite{ludwig2007} except ``95\% CI,'' which is
    calculated using the conventional asymptotic interval estimator.
    The last two rows list results from two robust procedures.}
  \label{tbl:2}
\end{table}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                   & ATE   & \multicolumn{2}{r}{95\% CI} & & $h$     & $b$ & p-value     \\
    \midrule                                                                          \\
    \multicolumn{5}{l}{Fraction ``high school or more'' (Panel A)}                    \\
    \midrule
    LM (2007)      & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
    CCT            & 0.055 & (0.013                      & 0.097) & 3&.671 & 8.618       \\
    Wild bootstrap & 0.055 & (0.010                      & 0.097) & 3&.671 & 8.618       \\\\
    \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
    \midrule
    LM (2007)      & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
    CCT            & 0.051 & (0.006                      & 0.096) & 5&.076 & 10.251      \\
    Wild bootstrap & 0.052 & (0.006                      & 0.092) & 5&.076 & 10.251      \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on education for cohort
    18--24 in 1990. Panel A uses the fraction of people with high school
    or more as dependent variable. Panel B uses the fraction of people
    with some college or more as dependent variable. The first row in
    each panel comes from Table 4 in \cite{ludwig2007} except ``95\% CI,''
    which is calculated using the conventional asymptotic interval estimator.
    The last two rows in
    each panel list results from two robust procedures.}
  \label{tbl:3}
\end{table}

>>>>

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                      & ATE     & \multicolumn{2}{r}{95\% CI}            &     &  $h$ &   $b$ & p-value \\
    \midrule
    LM (2007)         & --1.895 & (--3.930                    & 0.139)   & 9   &      &       & 0.036 \\
    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18  &      &       & 0.081 \\
    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
    CCT               & --3.795 & (--7.040                    & --0.551) & 3   & .888 & 6.807 &       \\ 
    Wild bootstrap    & --3.800 & (--6.781                    & --0.408) & 3   & .888 & 6.807 &       \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on mortality. The first three
    rows come from Table 3 in \cite{ludwig2007} except ``95\% CI,'' which is
    calculated using the conventional asymptotic interval estimator.
    The last two rows list results from two robust procedures.}
  \label{tbl:2}
\end{table}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                   & ATE   & \multicolumn{2}{r}{95\% CI} & & $h$     & $b$ & p-value     \\
    \midrule                                                                          \\
    \multicolumn{5}{l}{Fraction ``high school or more'' (Panel A)}                    \\
    \midrule
    LM (2007)      & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
    CCT            & 0.055 & (0.014                      & 0.096) & 3&.671 & 8.618       \\
    Wild bootstrap & 0.055 & (0.010                      & 0.097) & 3&.671 & 8.618       \\\\
    \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
    \midrule
    LM (2007)      & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
    CCT            & 0.051 & (0.004                      & 0.099) & 5&.076 & 10.251      \\
    Wild bootstrap & 0.052 & (0.006                      & 0.092) & 5&.076 & 10.251      \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on education for cohort
    18--24 in 1990. Panel A uses the fraction of people with high school
    or more as dependent variable. Panel B uses the fraction of people
    with some college or more as dependent variable. The first row in
    each panel comes from Table 4 in \cite{ludwig2007} except ``95\% CI,''
    which is calculated using the conventional asymptotic interval estimator.
    The last two rows in
    each panel list results from two robust procedures.}
  \label{tbl:3}
\end{table}
